Evaluación de impacto de la Reforma en Telecomunicaciones del 2013 en logro educativo en México

### 2021-05-11 final/pptx/presentacion.Rmd
update

.pull-left[
```{r,echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out6<- rdplot(cambio_esp_top,cambio_internet,nbins=c(20,20),x.lim=c(-25,50),x.label="Cambio Internet",y.label="Cambio Espanol",title="",kernel="triangular",c=15, binselect = "qspr")
```
]

@@

out7<- rdplot(cambio_mat_top,cambio_internet,nbins=c(20,20),x.lim=c(-10,50),y.lim=c(0,20),x.label="Cambio Internet",y.label="Cambio Mate",title="",c=15,kernel="triangular", binselect = "qspr")
```
]

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out = rdbwselect(cambio_esp_top, cambio_internet,c=15, kernel = "triangular", p = 1, bwselect = "mserd")
summary(out)
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out = rdbwselect(cambio_mat_top, cambio_internet,c=15, kernel = "triangular", p = 1, bwselect = "mserd")
summary(out)
```

@@

.pull-left[
```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out<-rdplot(data$cambio_esp_top,data$cambio_internet,nbins=c(20,20),x.lim=c(-10,40),title="",x.label="Cambio Internet",y.label="Cambio Espanol, kernel = "triangular",c=15,h=5,p=1 , binselect = "qspr")
```
]

.pull-right[
```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out<-rdplot(data$cambio_mat_top,data$cambio_internet,nbins=c(20,20),x.label="Cambio Internet",x.lim=c(-10,40),y.label="Cambio Mate, kernel = "triangular",c=15,h=7 ,p=1, binselect = "qspr")
```
]

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
Variable<-c("Promedio escolaridad", "Poblacion ocupada", "Nivel Marginacion")
Media.C<-c("1.006","43.928","1.903")
Media.T<-c("1.440", "44.620","1.855")
Diferencia<-c("0.434", "0.692","-0.048")
Valor.p<-c("0.00000", "0.0176","0.008")
kable(dataf, booktabs=T,format = "latex",col.names=c("Variable", "Media control", "Media Tratamiento","Diferencia","Valor-p")) %>% kable_styling(position = "center")
```

>>>>

.pull-left[
```{r,echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}

out7<- rdplot(cambio_esp_top,cambio_internet,nbins=c(20,20),x.lim=c(0,50),y.lim=c(0,20),x.label="Cambio Internet",y.label="Cambio Mate",title="",c=15,kernel="triangular", binselect = "qspr")
```
]

@@

out7<- rdplot(cambio_mat_top,cambio_internet,nbins=c(20,20),x.lim=c(-0,50),y.lim=c(0,20),x.label="Cambio Internet",y.label="Cambio Mate",title="",c=15,kernel="triangular", binselect = "qspr")
```
]

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out = rdbwselect(cambio_esp_top, cambio_internet,c=9, kernel = "triangular", p = 1, bwselect = "mserd")
summary(out)
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out = rdbwselect(cambio_mat_top, cambio_internet,c=9, kernel = "triangular", p = 1, bwselect = "mserd")
summary(out)
```

@@

.pull-left[
```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out<-rdplot(data$cambio_esp_top,data$cambio_internet,nbins=c(20,20),x.lim=c(-10,40),title="",x.label="Cambio Internet",y.label="Cambio Espanol", kernel = "triangular",c=9,h=4.572 ,p=1 , binselect = "qspr")
```
]

.pull-right[
```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
out<-rdplot(data$cambio_mat_top,data$cambio_internet,nbins=c(20,20),x.lim=c(-10,40),title="",x.label="Cambio Internet",y.label="Cambio Espanol", kernel = "triangular",c=9,h=4.183 ,p=1 , binselect = "qspr")
```
]

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE}
Variable<-c("Promedio escolaridad", "Poblacion ocupada", "Nivel Marginacion")
Media.C<-c("1.006","43.928","1.903")
Media.T<-c("1.440", "44.620","1.855")
Diferencia<-c("0.434", "0.692","-0.048")
Valor.p<-c("0.00000", "0.0176","0.008")
dataf<-data.frame(Variable, Media.C, Media.T,Diferencia,Valor.p, stringsAsFactors=TRUE)
kable(dataf, booktabs=T,format = "latex",col.names=c("Variable", "Media control", "Media Tratamiento","Diferencia","Valor-p")) %>% kable_styling(position = "center")
```
